A planetary collision afterglow and transit of the resultant debris cloud

### 2023-10-09 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
\begin{centering}
%\includegraphics[width=\columnwidth]{Size_cooling_combined_figure.pdf}
\caption{The size and temporal evolution of a post-impact body.
%
A post-impact body of a few to tens of Earth masses could be large enough to explain the observed increase in thermal emission from ASASSN-21qj and the subsequent infrared fluxes.
%
Panel {\bf a} shows the Hill radii for bodies at different semi-major axis (solid colored lines) and the Bondi radii (dotted lines) assuming different compositions for the vapor of the post-impact body.
%
The horizontal black dashed line shows the radii required to explain the observed flux at the inferred emission temperature of 1000~K. 
%
The change in excess flux due to a post-impact body with time for a simple model of cooling of a post-impact body for different power-law surface density profiles is in panel {\bf b}, eqn~\ref{eqn:sigma} and for different mass bodies in panel {\bf c}.
%
Each example had an initial radius of 7\,$R_\odot$, a radiative temperature of 1000~K, and a corresponding initial flux of 0.04\,$L_\star$, as estimated for the observed infrared emittor.
%
The solid lines are profiles that can have non-zero initial density at the initial emitting radius, and the dashed lines are for ones that are forced to have zero density at the initial emitting radius.
%
When not stated, the mass of the post-impact body was 50~$M_{\rm Earth}$, the power law exponent is $-2$, and the size of the central region was 10~$R_{\rm Earth}$.
}
\label{fig:Hill_Bondi_R}
\end{centering}
\end{figure}

@@

\bmhead{Availability of data and materials}
The data sets generated and analysed during the current study are available in the Zenodo repository XXXX CHANGE TO FINAL ZENODO PLACE ON ACCEPTANCE \url{https://sandbox.zenodo.org/record/1180221}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=\columnwidth]{figures/Size_cooling_combined_figure.pdf}
\caption{The size and temporal evolution of a post-impact body.
%
A post-impact body of a few to tens of Earth masses could be large enough to explain the observed increase in thermal emission from ASASSN-21qj and the subsequent infrared fluxes.
%
Panel {\bf a} shows the Hill radii for bodies at different semi-major axis (solid colored lines) and the Bondi radii (dotted lines) assuming different compositions for the vapor of the post-impact body.
%
The horizontal black dashed line shows the radii required to explain the observed flux at the inferred emission temperature of 1000~K. 
%
The change in excess flux due to a post-impact body with time for a simple model of cooling of a post-impact body for different power-law surface density profiles is in panel {\bf b}, eqn~\ref{eqn:sigma} and for different mass bodies in panel {\bf c}.
%
Each example had an initial radius of 7\,$R_\odot$, a radiative temperature of 1000~K, and a corresponding initial flux of 0.04\,$L_\star$, as estimated for the observed infrared emittor.
%
The solid lines are profiles that can have non-zero initial density at the initial emitting radius, and the dashed lines are for ones that are forced to have zero density at the initial emitting radius.
%
When not stated, the mass of the post-impact body was 50~$M_{\rm Earth}$, the power law exponent is $-2$, and the size of the central region was 10~$R_{\rm Earth}$.
}
\label{fig:Hill_Bondi_R}
\script{plot_hill_bondi_radii_three_panels.py}

\end{centering}
\end{figure}

@@

\bmhead{Availability of data and materials}
The data sets generated and analysed during the current study are available in the Zenodo repository \url{https://zenodo.org/record/8344755}
